Prepare Data

### 2021-10-19 src/analysis/analyses.Rmd
add code

```{r "data for analyses",  eval = F}
source(here("src/analysis/data-for-analyses.R"))
```

## Check Missing Values
I employ the following criteria:

- If 10% or less of the values on the dimension are missing, then we re-code the missing values to the overall mean.
- If 11% or more of the values on the dimension are missing, then we re-code the missing values to a constant (for instance 0) and include a dummy variable indicating whether the response on the covariate was missing or not.

```{r "check missings",  eval = F}
descr <- d %>%
  summarise(`DV: Trait Evaluation` = round(sum(is.na(PT1))/n(),4),
            `DV: Favorability` = round(sum(is.na(PT2))/n(),4),
            `DV: Representation` = round(sum(is.na(PT3))/n(),4),
            `DV: Career Prospects` = round(sum(is.na(PT4))/n(),4),
            `Immigration (%)` = round(sum(is.na(PreT1))/n(),4),
            `Position: Immigration` = round(sum(is.na(PreT2))/n(),4),
            `Position: Defense` = round(sum(is.na(PreT3))/n(),4),
            `Position: Education` = round(sum(is.na(PreT4))/n(),4),
            `Attitude: Women in Politics` = round(sum(is.na(PreT5))/n(),4),
            `Ideology` = round(sum(is.na(PreT6))/n(),4),
            `Political Efficacy (1)` = round(sum(is.na(PreT7_1))/n(),4),
            `Political Efficacy (2)` = round(sum(is.na(PreT7_2))/n(),4),
            `Political Efficacy (3)` = round(sum(is.na(PreT7_3))/n(),4),
            `Political Efficacy (4)` = round(sum(is.na(PreT7_4))/n(),4),
            `Political Efficacy (5)` = round(sum(is.na(PreT7_5))/n(),4),
            `Political Efficacy (6)` = round(sum(is.na(PreT7_6))/n(),4),
            `Political Efficacy (7)` = round(sum(is.na(PreT7_7))/n(),4),
            `Position: COVID-19` = round(sum(is.na(PreT8))/n(),4),
            `Gender` = round(sum(is.na(F1))/n(),4),
            `Age` = round(sum(is.na(F2))/n(),4),
            `Region` = round(sum(is.na(F3))/n(),4),
            `Urbaness` = round(sum(is.na(F4))/n(),4),
            `Migration Background` = round(sum(is.na(F5))/n(),4),
            `Party Preference` = round(sum(is.na(F6))/n(),4),
            `Employment` = round(sum(is.na(F7))/n(),4),
            `Income` = round(sum(is.na(F8))/n(),4),
            `Education` = round(sum(is.na(F9))/n(),4)) %>%
  pivot_longer(cols = `DV: Trait Evaluation`:`Education`,
              names_to = "Variables", values_to = "% Missing Values") %>%
  filter(`% Missing Values` > 0)

kable(descr) %>%
  kable_styling(full_width = F, position = "center")
```

I recode the missing values of the variables `Urbaness`, `Migration Background`, `Income`, and `Education` to the mean value of the respective variables.

```{r "add missings",  eval = F}
d <- d %>%
  mutate(F4 = replace_na(F4, round(mean(F4, na.rm = T),0)),
         F5 = replace_na(F5, round(mean(F5, na.rm = T),0)),
         F8 = replace_na(F8,round(mean(F8, na.rm = T),0)),
         F9 = replace_na(F9,round(mean(F9, na.rm = T),0)))
rm(descr, scales)
```

@@

## Descriptive Results
```{r "descriptive-results",  eval = F,echo=FALSE, fig.height=15, fig.width=10}
d %>%
  select(PT1, PT2, PT3, PT4, issue, name, compromise) %>%
  mutate(PT1 = PT1 * 2) %>%
  pivot_longer(cols = PT1:PT4,
               names_to = "dvs") %>%
  mutate(dvs = recode(dvs,
                      `PT1` = "DV: Trait Evaluation",
                      `PT2` = "DV: Favorability",
                      `PT3` = "DV: Representation",
                      `PT4` = "DV: Career Prospects"),
         compromise = if_else(compromise==1, "Compromise", "No Compromise"),
         compromise = factor(compromise,
                             level = c("No Compromise", "Compromise"))) %>%
  unite("treatment", c("issue", "name"), sep = ": ") %>%
  group_by(treatment, compromise, dvs) %>%
  summarise(means = round(mean(value, na.rm=T),1),
            stdev = sd(value, na.rm=T)) %>%
  mutate(lower = means - (1.56 * stdev),
         upper = means + (1.56 * stdev),
         type = if_else(means <= 5, "below", "above")) %>%
  ggplot(aes(x = treatment, 
             y =means, label = means, color=type,
             ymin = lower, ymax = upper)) +
  geom_point(stat='identity', size=6)  +
  scale_color_manual(values = c("above"=fig_cols[3],
                                "below"=fig_cols[2])) +
  geom_errorbar(width = 0) +
  geom_text(color="white", size=2) +
  facet_grid(dvs~compromise) +
  labs(y = "0 (negative) - 10 (positive)", 
       x = "", title = "Bend or Break") +
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5),
        legend.position="none",
        legend.title = element_blank(),
        axis.text=element_text(size=8)) +
  geom_hline(yintercept = 5, linetype = "dotted", color = "darkgrey") +
  coord_flip() 
```

@@

The figure below shows that the data is unbalanced for the variables: `Education`,`Income`, `Employment`, `Urbaness`, `Age`, `Position: COVID`, `Political Efficacy`, `Ideology`,
`Attitudes: Women in Politics`, `Position: Education`, `Position: Defense`, `Position: Immigration`, and `Immigration (%)`.
As described in the Pre-Analysis Plan (p.10), I will add these covariates to the analyses as controls.

@@

## Ethnic Conception Hypothesis 
```{r "h1",  eval = F, fig.align="center", fig.height=8, fig.width=8}
source(here("src/analysis/h1.R"))
p1
```

>>>>

```{r "data for analyses",  eval = F}
load(here("data/intermediate/cleaned_experiment.RData"))
source(here("src/analysis/data-for-analyses.R"))
```

@@

```{r "Table with Descriptives"}
source(here("src/analysis/descriptive-information-overview.R"))
table2 <- knitr::kable(descr, digits=2)
fn <- here("report/figures/table_descriptives.tex")
cat("# Table: Descriptive Information of Variables under Study \n\n", file=fn)
cat(table2, file=fn, sep="\n", append=T)

methodnames <- setNames(as.list(descr$Variables), descr$Variables)
table <- purrr::map(descr, .f= ".") 
#render_j2(here("src/analysis/table_descriptives.tex.j2"), here("report/figures/table_descriptives.tex"),
#          data=list(data=table, methods=methodnames))
rm(descr, methodnames, table, fn, table2)
```

## Descriptive Results
```{r "descriptive-results",  eval = F,echo=FALSE, fig.height=15, fig.width=10}
d %>%
  select(POST_2, POST_3, POST_4, ethnic) %>%
  pivot_longer(cols = POST_2:POST_4,
               names_to = "dvs") %>%
  mutate(dvs = recode(dvs,
                      `POST_2` = "DV: Item 2",
                      `POST_3` = "DV: Item 3",
                      `POST_4` = "DV: Item 4"),
         ethnic = if_else(ethnic==0, "Civic Conception", "Ethnic Conception")) %>%
  group_by(ethnic, dvs) %>%
  summarise(means = round(mean(value, na.rm=T),1),
            stdev = sd(value, na.rm=T)) %>%
  mutate(lower = means - (1.56 * stdev),
         upper = means + (1.56 * stdev),
         type = if_else(means <= 5, "below", "above")) %>%
  ggplot(aes(x = ethnic, 
             y =means, label = means,
             ymin = lower, ymax = upper)) +
  geom_point(stat='identity', size=6)  +
  scale_color_manual(values = c("above"=fig_cols[3],
                                "below"=fig_cols[2])) +
  geom_errorbar(width = 0) +
  geom_text(color="white", size=2) +
  facet_grid(dvs~.) +
  labs(y = "0 (negative) - 5 (positive)", 
       x = "", title = "The People as 'Volk' or 'Bürger'?") +
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5),
        legend.position="none",
        legend.title = element_blank(),
        axis.text=element_text(size=8)) +
  geom_hline(yintercept = 5, linetype = "dotted", color = "darkgrey") +
  coord_flip() 
```

@@

The figure below shows that the data is unbalanced for the variables: `Education`,`Income`, `Employment`, `Urbaness`, `Living Place`, `Birth Place`, `Age`, `Political Knowledge`, `Political Interest`, and `Ideology`.
As described in the Pre-Analysis Plan (p.10), I will add these covariates to the analyses as controls.

@@

## Ethnic Conception Hypothesis 
```{r "h1", fig.align="center", fig.height=8, fig.width=8}
source(here("src/analysis/h1.R"))
p1
```

### 2021-10-19 src/data-processing/prep_data.Rmd
update
add code

```{r "get data from Qualtrics", results="hide"}
d <- fetch_survey(surveyID = "SV_7PoXOEVMUF1JZn8", 
                    verbose = TRUE, force_request = T,
                    label = FALSE, convert = FALSE)
source(here("src/data-processing/clean_data.R"))
```

## Save Data for Analysis
```{r "save data",eval=FALSE}
save(d, file = here("data/intermediate/cleaned_data.RData"))
```

@@

### Correlations Matrix
```{r "Correlations Matrix", eval = F, echo=F, message=T, warning=T, fig.width=15, fig.height=15}
d %>%
  select(`Gender` = F1,
         `Age` = F2,
         `Education` = F9,
         `Region`  = F3,
         `Urbanness`  = F4,
         `Migration Background`  = F5,
         `Job`  = F7,
         `Income`  = F8,
         `Position: Immigration (%)`  = PreT1,
         `Position: Immigration`  = PreT2,
         `Position: Defense`  = PreT3,
         `Position: Education`  = PreT4,
         `Position: Attitude Women in Politics`  = PreT5,
         `Ideology`  = PreT6,
         `Political Efficacy` = PreT7, 
         `Position: COVID-19 Policy` = PreT8,
         `DV: Trait Evaluation` = PT1,
         `DV: Favorability` = PT2,
         `DV: Representation` = PT3,
         `DV: Career Prospects` = PT4) %>%
  ggcorrmat(
  type = "robust", # correlation method
  cor.vars = c(everything()), # a range of variables can be selected
  colors = c(fig_cols[1], fig_cols[4], fig_cols[8]),
  title = "Correlalogram for Variables under Study"
)
```

>>>>

```{r "get data from Qualtrics", results="hide"}
## Match data with RESPONDI quota questions
d <- fetch_survey(surveyID = "SV_7PoXOEVMUF1JZn8", 
                    verbose = TRUE, force_request = T,
                    label = FALSE, convert = FALSE)
source(here("src/data-processing/clean_data.R"))
```

## Save Data for Analysis
```{r "save data",eval=FALSE}
save(d, file = here("data/intermediate/cleaned_experiment.RData"))
```

@@

### Correlations Matrix
```{r "Correlations Matrix", echo=F, message=T, warning=T, fig.width=15, fig.height=15}
d %>%
  mutate(HT4 = (HT4_1 + HT4_2 + HT4_3 + HT4_4)/4) %>%
  select(#`Gender` = D1,
         #`Age` = D2,
         #`Education` = D3,
         `Region`  = D9,
         `Birth-place` = D10,
         `Urbanness`  = D4,
         `Job`  = D7,
         `Income`  = D8,
         `Political Knowledge (1)`  = PT4,
         `Political Knowledge (2)`  = PT5,
         `Political Knowledge (3)`  = PT6,
         `Political Interest`  = PT7,
         `Ideology`  = PT8,
         `Exclusive National Identity` = HT4) %>%
  ggcorrmat(
  type = "robust", # correlation method
  cor.vars = c(everything()), # a range of variables can be selected
  colors = c(fig_cols[1], fig_cols[4], fig_cols[8]),
  title = "Correlalogram for Variables under Study"
)
```
